The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-26 paper.tex
work in progress... review of neuro literature focused on human-robot interaction and some very early attempt to integrate to the model 3 stages

In this section, we discuss more speculative aspects and hypotheses that follow
from the model. These aspects would benefit further investigations and
experimental support.

\subsection{Cognitive Interpretations}
\label{sec:cognitive-model}

@@

We provide in this section a tentative interpretation of anthropomorphism in
terms of cognitive correlates. We warmly welcome the feedback and
comments from both the cognitive sciences and robotics communities to further
discuss these findings.

@@

\subsection{Cognitive Processes and Phases}

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
Anthropomorphism at this pre-cognitive stage might also be mediated by the
human's mirror neurons system (neurons that fire both during execution of
specific goal-oriented action and during the viewing of action directed toward
the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
the robot's goal-directed actions into the human own motor
repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}. Interestingly
\citet{Gazzola2007} have found no significant difference in the activation of
the mirror neurons system during the observation of an industrial robot or of a
human performing the same action, supporting the hypothesis that the goal of the
action is more important than its kinematics to activate mirror neurons.

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}).

@@

This mental process depends on the human understanding of the robot's
inner working, as well as his/her own tendency to anthropomorphize (the
\emph{personality} in ICA factor), but at this
stage, the \emph{perception} of the robot (its shape for instance) and its
intended \emph{purpose} play a less important role. It is mostly a human-centric
process.  The result of this third phase would be an iteratively adapted
cognitive model of the robot.

>>>>

In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
We then discuss more speculative aspects and hypotheses that follow
from the model. These aspects would benefit further investigations and
experimental support.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%    Review of neuroscience work on robot-based 
%    anthropomorphism..... may be moved somewhere 
%    else or dispatched

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
The neuroscientific study of human-robot interaction is still in its infancy. So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref). 
We briefly review below the neuroscientific literature relevant to understand the neural basis of anthropomorphism.

%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.

\paragraph{Anthropomorphic response to motor behavior \\}
Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.

There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms. %mirror neurons

%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.

\paragraph{Anthropomorphism and social behaviour}
In studying emotional perception in a human or a robot face using functional magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties. However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expresion, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.

Howver, using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.

%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie. wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).

Finally, individual tendency to anthropomorphize has been related to the grey matter volume of a brain area involved in mentalizing - the attribution of mental states to other human beings \citet{cullen2013individual, Frith2003}.

Thus it seems that the display of resonance mechanisms for social behaviour in a human-robot interaction is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism . Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}

%\paragraph{Emotions/Empathy}
%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.

In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates. We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
discuss these findings.

\subsection{Cognitive model}
\label{sec:cognitive-model}

@@

@@

\subsubsection{Cognitive Processes and Phases}

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonnance mechanisms at the neuronal level.

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}). At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.

@@

This mental process depends on the human understanding of the robot's
inner working, as well as his/her own tendency to anthropomorphize (the
\emph{personality} in ICA factor), but at this
stage, the \emph{perception} of the robot (its shape for instance) and its
intended \emph{purpose} play a less important role. It is mostly a human-centric
process.  The result of this third phase would be an iteratively adapted
cognitive model of the robot. It is also at this last stage that the human might modified its own abilities to anthropomorphize, having built a full cognitive model of the robot and know being able to attribute internal state to the robot.
